\Title

### 2021-01-27 manuscript/manuscript.tex
Add some text to the appendix with the tables

\noindent
\textbf{Keywords:}
Gravity anomalies and Earth structure;
Magnetic anomalies: modelling and interpretation;
Geopotential theory;
Inverse theory;
Statistical methods;
Australia;

\begin{abstract}
  The equivalent source technique is a powerful and widely used method for
  processing gravity and magnetic data.  Nevertheless, it has the major
  drawback of having a large computational cost in terms of processing time and
  computer memory.
  We present two techniques for reducing the computational cost of equivalent
  source processing: block-averaging source locations and the
  gradient-boosted equivalent source algorithm.
  By using block-averaging, we reduce the number of source coefficients that
  must be estimated while retaining the minimum desired resolution in the final
  processed data.
  With the gradient boosting method, we estimate the layer coefficients in
  small batches along overlapping windows, allowing us to reduce the computer
  memory requirements arbitrarily to conform to the constraints of the
  available hardware.
  We show that the combination of block-averaging and gradient-boosted
  equivalent sources are capable of producing accurate interpolations through
  tests against synthetic data.
  Moreover, we demonstrate the feasibility of our method by gridding a gravity
  dataset covering Australia with over 1.7 million observations using a modest
  personal computer in under two hours of total processing time.
\end{abstract}

@@

\subsection{Source distribution strategies}

@@

\section{Source distributions parameters}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey. The table also contains the set of parameters
        that generates the best prediction for each source distribution and its
        corresponding RMS score (in mGal).
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{RMS} \\
        \toprule

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant}
                & Depth (m)
                & \GroundSourceBelowDataConstantDepthDepth
                & \BestGroundSourceBelowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBelowDataConstantDepthRms
                  } \\
            &
                & Damping
                & \GroundSourceBelowDataConstantDepthDamping
                & \BestGroundSourceBelowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative}
                & Depth (m)
                & \GroundSourceBelowDataRelativeDepthDepth
                & \BestGroundSourceBelowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBelowDataRelativeDepthRms
                  } \\
            &
                & Damping
                & \GroundSourceBelowDataRelativeDepthDamping
                & \BestGroundSourceBelowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable}
                & Depth (m)
                & \GroundSourceBelowDataVariableDepthDepth
                & \BestGroundSourceBelowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestGroundSourceBelowDataVariableDepthRms
                  } \\
            &
                & Depth factor
                & \GroundSourceBelowDataVariableDepthDepthFactor
                & \BestGroundSourceBelowDataVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundSourceBelowDataVariableDepthKNearest
                & \BestGroundSourceBelowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \GroundSourceBelowDataVariableDepthDamping
                & \BestGroundSourceBelowDataVariableDepthDamping
                & \\
        \midrule

        \multirow{11}{*}{Block Averaged Sources}
            & \multirow{3}{*}{Constant}
                & Depth (m)
                & \GroundBlockAveragedSourcesConstantDepthDepth
                & \BestGroundBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesConstantDepthSpacing
                & \BestGroundBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesConstantDepthDamping
                & \BestGroundBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative}
                & Depth (m)
                & \GroundBlockAveragedSourcesRelativeDepthDepth
                & \BestGroundBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesRelativeDepthRms
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesRelativeDepthSpacing
                & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesRelativeDepthDamping
                & \BestGroundBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable}
                & Depth (m)
                & \GroundBlockAveragedSourcesVariableDepthDepth
                & \BestGroundBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestGroundBlockAveragedSourcesVariableDepthRms
                  } \\
            &
                & Depth factor
                & \GroundBlockAveragedSourcesVariableDepthDepthFactor
                & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundBlockAveragedSourcesVariableDepthKNearest
                & \BestGroundBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesVariableDepthSpacing
                & \BestGroundBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesVariableDepthDamping
                & \BestGroundBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant}
                & Depth (m)
                & \GroundGridSourcesConstantDepthDepth
                & \BestGroundGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestGroundGridSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \GroundGridSourcesConstantDepthSpacing
                & \BestGroundGridSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundGridSourcesConstantDepthDamping
                & \BestGroundGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey. The table also contains the set of
        parameters that generates the best prediction for each source
        distribution and its corresponding RMS score (in mGal).
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{RMS} \\
        \toprule

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant}
                & Depth (m)
                & \AirborneSourceBelowDataConstantDepthDepth
                & \BestAirborneSourceBelowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestAirborneSourceBelowDataConstantDepthRms
                  } \\
            &
                & Damping
                & \AirborneSourceBelowDataConstantDepthDamping
                & \BestAirborneSourceBelowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative}
                & Depth (m)
                & \AirborneSourceBelowDataRelativeDepthDepth
                & \BestAirborneSourceBelowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestAirborneSourceBelowDataRelativeDepthRms
                  } \\
            &
                & Damping
                & \AirborneSourceBelowDataRelativeDepthDamping
                & \BestAirborneSourceBelowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable}
                & Depth (m)
                & \AirborneSourceBelowDataVariableDepthDepth
                & \BestAirborneSourceBelowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneSourceBelowDataVariableDepthRms
                  } \\
            &
                & Depth factor
                & \AirborneSourceBelowDataVariableDepthDepthFactor
                & \BestAirborneSourceBelowDataVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneSourceBelowDataVariableDepthKNearest
                & \BestAirborneSourceBelowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \AirborneSourceBelowDataVariableDepthDamping
                & \BestAirborneSourceBelowDataVariableDepthDamping
                & \\
        \midrule

        \multirow{11}{*}{Block Averaged Sources}
            & \multirow{3}{*}{Constant}
                & Depth (m)
                & \AirborneBlockAveragedSourcesConstantDepthDepth
                & \BestAirborneBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesConstantDepthSpacing
                & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesConstantDepthDamping
                & \BestAirborneBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative}
                & Depth (m)
                & \AirborneBlockAveragedSourcesRelativeDepthDepth
                & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesRelativeDepthRms
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesRelativeDepthSpacing
                & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesRelativeDepthDamping
                & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable}
                & Depth (m)
                & \AirborneBlockAveragedSourcesVariableDepthDepth
                & \BestAirborneBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestAirborneBlockAveragedSourcesVariableDepthRms
                  } \\
            &
                & Depth factor
                & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneBlockAveragedSourcesVariableDepthKNearest
                & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesVariableDepthSpacing
                & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesVariableDepthDamping
                & \BestAirborneBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant}
                & Depth (m)
                & \AirborneGridSourcesConstantDepthDepth
                & \BestAirborneGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneGridSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \AirborneGridSourcesConstantDepthSpacing
                & \BestAirborneGridSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneGridSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

>>>>

\begin{abstract}
    My abstract
    \\[0.5cm]
    \textbf{Keywords:}
    My keywords
\end{abstract}

@@

\subsection{Source distribution strategies}
\label{sec:synthetic_distributions}

@@

\section{Source position parameters used for the tests on synthetic data}

Tables~\ref{tab:parameters-ground-survey}
and~\ref{tab:parameters-airborne-survey} show the parameter values tested and
their optimal values for creating the equivalent source distributions tested in
Section~\ref{sec:synthetic_distributions}.
The optimal values were used to produce the results in
Figs~\ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences}.

\begin{table*}
    \centering
    \caption{
        Parameters used to produce each source distribution for interpolating
        the synthetic ground survey data. Also contains the set of parameters
        that generates the smallest RMS error for each source distribution and
        their corresponding RMS.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{RMS} \\
        \toprule

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant}
                & Depth (m)
                & \GroundSourceBelowDataConstantDepthDepth
                & \BestGroundSourceBelowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBelowDataConstantDepthRms
                  } \\
            &
                & Damping
                & \GroundSourceBelowDataConstantDepthDamping
                & \BestGroundSourceBelowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative}
                & Depth (m)
                & \GroundSourceBelowDataRelativeDepthDepth
                & \BestGroundSourceBelowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBelowDataRelativeDepthRms
                  } \\
            &
                & Damping
                & \GroundSourceBelowDataRelativeDepthDamping
                & \BestGroundSourceBelowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable}
                & Depth (m)
                & \GroundSourceBelowDataVariableDepthDepth
                & \BestGroundSourceBelowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestGroundSourceBelowDataVariableDepthRms
                  } \\
            &
                & Depth factor
                & \GroundSourceBelowDataVariableDepthDepthFactor
                & \BestGroundSourceBelowDataVariableDepthDepthFactor
                & \\
            &
                & $k$ neighbours
                & \GroundSourceBelowDataVariableDepthKNearest
                & \BestGroundSourceBelowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \GroundSourceBelowDataVariableDepthDamping
                & \BestGroundSourceBelowDataVariableDepthDamping
                & \\
        \midrule

        \multirow{11}{*}{Block Averaged Sources}
            & \multirow{3}{*}{Constant}
                & Depth (m)
                & \GroundBlockAveragedSourcesConstantDepthDepth
                & \BestGroundBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesConstantDepthRms
                  } \\
            &
                & Block size (m)
                & \GroundBlockAveragedSourcesConstantDepthSpacing
                & \BestGroundBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesConstantDepthDamping
                & \BestGroundBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative}
                & Depth (m)
                & \GroundBlockAveragedSourcesRelativeDepthDepth
                & \BestGroundBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesRelativeDepthRms
                  } \\
            &
                & Block size (m)
                & \GroundBlockAveragedSourcesRelativeDepthSpacing
                & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesRelativeDepthDamping
                & \BestGroundBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable}
                & Depth (m)
                & \GroundBlockAveragedSourcesVariableDepthDepth
                & \BestGroundBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestGroundBlockAveragedSourcesVariableDepthRms
                  } \\
            &
                & Depth factor
                & \GroundBlockAveragedSourcesVariableDepthDepthFactor
                & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & $k$ neighbours
                & \GroundBlockAveragedSourcesVariableDepthKNearest
                & \BestGroundBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Block size (m)
                & \GroundBlockAveragedSourcesVariableDepthSpacing
                & \BestGroundBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesVariableDepthDamping
                & \BestGroundBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant}
                & Depth (m)
                & \GroundGridSourcesConstantDepthDepth
                & \BestGroundGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestGroundGridSourcesConstantDepthRms
                  } \\
            &
                & Grid spacing (m)
                & \GroundGridSourcesConstantDepthSpacing
                & \BestGroundGridSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundGridSourcesConstantDepthDamping
                & \BestGroundGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used to produce each source distribution for interpolating
        the synthetic airborne survey data. Also contains the set of parameters
        that generates the smallest RMS error for each source distribution and
        their corresponding RMS.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{RMS} \\
        \toprule

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant}
                & Depth (m)
                & \AirborneSourceBelowDataConstantDepthDepth
                & \BestAirborneSourceBelowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestAirborneSourceBelowDataConstantDepthRms
                  } \\
            &
                & Damping
                & \AirborneSourceBelowDataConstantDepthDamping
                & \BestAirborneSourceBelowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative}
                & Depth (m)
                & \AirborneSourceBelowDataRelativeDepthDepth
                & \BestAirborneSourceBelowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestAirborneSourceBelowDataRelativeDepthRms
                  } \\
            &
                & Damping
                & \AirborneSourceBelowDataRelativeDepthDamping
                & \BestAirborneSourceBelowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable}
                & Depth (m)
                & \AirborneSourceBelowDataVariableDepthDepth
                & \BestAirborneSourceBelowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneSourceBelowDataVariableDepthRms
                  } \\
            &
                & Depth factor
                & \AirborneSourceBelowDataVariableDepthDepthFactor
                & \BestAirborneSourceBelowDataVariableDepthDepthFactor
                & \\
            &
                & $k$ neighbours
                & \AirborneSourceBelowDataVariableDepthKNearest
                & \BestAirborneSourceBelowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \AirborneSourceBelowDataVariableDepthDamping
                & \BestAirborneSourceBelowDataVariableDepthDamping
                & \\
        \midrule

        \multirow{11}{*}{Block Averaged Sources}
            & \multirow{3}{*}{Constant}
                & Depth (m)
                & \AirborneBlockAveragedSourcesConstantDepthDepth
                & \BestAirborneBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesConstantDepthRms
                  } \\
            &
                & Block size (m)
                & \AirborneBlockAveragedSourcesConstantDepthSpacing
                & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesConstantDepthDamping
                & \BestAirborneBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative}
                & Depth (m)
                & \AirborneBlockAveragedSourcesRelativeDepthDepth
                & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesRelativeDepthRms
                  } \\
            &
                & Block size (m)
                & \AirborneBlockAveragedSourcesRelativeDepthSpacing
                & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesRelativeDepthDamping
                & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable}
                & Depth (m)
                & \AirborneBlockAveragedSourcesVariableDepthDepth
                & \BestAirborneBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestAirborneBlockAveragedSourcesVariableDepthRms
                  } \\
            &
                & Depth factor
                & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & $k$ neighbours
                & \AirborneBlockAveragedSourcesVariableDepthKNearest
                & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Block size (m)
                & \AirborneBlockAveragedSourcesVariableDepthSpacing
                & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesVariableDepthDamping
                & \BestAirborneBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant}
                & Depth (m)
                & \AirborneGridSourcesConstantDepthDepth
                & \BestAirborneGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneGridSourcesConstantDepthRms
                  } \\
            &
                & Grid spacing (m)
                & \AirborneGridSourcesConstantDepthSpacing
                & \BestAirborneGridSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneGridSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}
